paper

### 2024-09-18 paper.qmd
.

# Set metadata and formula for LimROTS analysis
meta.info <- c("mixing.ratio" , "fake.batch")
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case3)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30   # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio + fake.batch"  # Formula for group comparison

# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = BM21.Case3, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)
```

>>>>

# Set metadata and formula for LimROTS analysis
meta.info <- c("mixing.ratio" , "fake.batch")
B <- 1000  # Number of bootstrap samples
K <- dim(BM21.Case3)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30   # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "mixing.ratio"
formula.str <- "~ 0 + mixing.ratio + fake.batch"  # Formula for group comparison

# Run LimROTS analysis with trend and robust settings enabled
limrots.result <- LimROTS(data.exp = BM21.Case3, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE)

limrots.result.df <- data.frame(row.names = row.names(limrots.result$data), q.value = limrots.result$q_values$qvalues , fdr = limrots.result$FDR,
                                bh = limrots.result$BH.pvalue , fc = limrots.result$corrected.logfc)

length(which(limrots.result.df$q.value < 0.05))
length(which(limrots.result.df$fdr < 0.05))

limrots.result.df <- limrots.result.df[limrots.result.df$q.value < 0.05,]

length(which(grepl("_pluseffect", row.names(limrots.result.df)) ))

length(which(grepl("synthetic", row.names(limrots.result.df)) ))
```
